Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-09-11 2019/NUMTA_Barkalov/LNCS/numta19.tex
Italic font for Simple and Hard

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_4.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_4.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS Simple (a) and Hard (b) classes, $N=4$.}
\label{oper4}
\end{figure}

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_5.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_5.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS Simple (a) and Hard (b) classes, $N=5$.}
\label{oper5}
\end{figure}

>>>>

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_4.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_4.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=4$.}
\label{oper4}
\end{figure}

\begin{figure}
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklss_5.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
\center{\includegraphics[width=1.0\linewidth]{Operating_characteristic_gklsh_5.png} \\ (b)}
\end{minipage}
\caption{Operational characteristics for GKLS \textit{Simple} (a) and \textit{Hard} (b) classes, $N=5$.}
\label{oper5}
\end{figure}
